---
title: "DEB analysis with MI"
output: html_document
date: "2025-02-13"
---

#Load Packages
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

#packages
#install.packages("foreign")
#install.packages("effects")
#install.packages("mediation")
#install.packages("bruceR")
#install.packages("naniar")
#install.packages("VIM")
library(VIM)
library(naniar)
library(bruceR)
library(foreign)
library(dplyr)
library(psych)
library(ggplot2)
library(car)
library(effects)
library(lavaan)
library(kableExtra)
library(broom)
library(tidyverse)
library(gridExtra)
library(mice)
library(miceadds)
source("PROCESS v4.3 for R/process.R")
```

#Load Data
```{r}
#load data
avon.data <- foreign::read.spss("Data_2.sav", to.data.frame = TRUE, reencode = TRUE)
head(avon.data)
```


#Create new table with age, gender, memory specificity, disordered eating behaviours
```{r}

# ccm991a = age
# kz021 = sex
# c645a = education
# c804 = ethnicity

data <- avon.data[, c("cidB3980","ccm991a", "kz021","c804", "a_happ_5g", "b_bore_5g", "c_reli_5g", "d_hope_5g","e_exci_5g", "f_fail_5g", "g_lone_5g", "h_sad_5g", "i_luck_5g", "j_rela_5g", "ccs5520", "ccs5530", "ccs5540", "ccs5541","ccs5510","ccs5511","ccs5512","ccs5513","ccs5550","ccs5560", "ccs3000","ccs3001", "ccs3002","ccs3003","ccs3004","ccs3005","ccs3006","ccs3007","ccs3008","ccs3009","ccs3010","ccs3011","cct4105","cct4106","cct4107","cct4108","cct4110","cct4112","cct4115","cct4116","cct4120","cct4125","ccs4500", "ccs4502", "ccs4503", "ccs4504", "ccs4505", "ccs4506", "ccs4508", "ccs4509","ccs4511", "ccs4512", "ccs4513", "ccs4514", "ccs4515","c645a","ccs5583")]

data <- rename(data, ID = cidB3980)
data <- rename(data, Sex = kz021)
data <- rename(data, Ethnicity = c804)
data <- rename(data, Age = ccm991a)


show(data)
```

# Count the number of specific memories
```{r}


data1 <- data %>%
  mutate(PosAMS = rowSums(select(.,
    c(
      "a_happ_5g",
      "c_reli_5g",
      "e_exci_5g",
      "i_luck_5g",
      "j_rela_5g"
    )
  ) == "4. specific", na.rm = FALSE)) %>%
  mutate(NegAMS = rowSums(select(.,
    c("b_bore_5g", "d_hope_5g", "f_fail_5g", "g_lone_5g", "h_sad_5g")
  ) == "4. specific", na.rm = FALSE)) %>%
  mutate(AMStotal = rowSums(select(.,
    c(
      "a_happ_5g",
      "b_bore_5g",
      "c_reli_5g",
      "d_hope_5g",
      "e_exci_5g",
      "f_fail_5g",
      "g_lone_5g",
      "h_sad_5g",
      "i_luck_5g",
      "j_rela_5g"
    )
  ) == "4. specific", na.rm = FALSE))


data1
describeData1 <- describe(data1)
describe
summaryData1 <- summary(data1)
view(summaryData1)
```




# Coding LOC
```{r}
# Locus of control data
# ccs3000 - ccs3011 = loc data

LoC <- data [, c("ID","ccs3000","ccs3001", "ccs3002","ccs3003","ccs3004","ccs3005","ccs3006","ccs3007","ccs3008","ccs3009","ccs3010","ccs3011")]
LoC
describe(LoC)
```


```{r}
# Coding Locus of control data
data2 <- data1 %>%
  mutate(across(ccs3000:ccs3010, ~ifelse(. == "Yes", 1, 0)),
         ccs3011 = ifelse(ccs3011 == "No", 1, 0)) %>%
  select(-c(a_happ_5g, b_bore_5g, c_reli_5g, d_hope_5g,e_exci_5g, f_fail_5g, g_lone_5g, h_sad_5g, i_luck_5g, j_rela_5g)) 
data2
summary(data2)
```

```{r}
# Adding total LoC scores
Total_LoC <- rowSums(data2[,c("ccs3000","ccs3001","ccs3002","ccs3003","ccs3004","ccs3005","ccs3006","ccs3007","ccs3008","ccs3009","ccs3010","ccs3011")])
Total_LoC[!complete.cases(data2[,c("ccs3000","ccs3001","ccs3002","ccs3003","ccs3004","ccs3005","ccs3006","ccs3007","ccs3008","ccs3009","ccs3010","ccs3011")])] <- NA
data2$Total_LoC <- Total_LoC
head(data2)

```

# Recoding depressive symptoms at age 16
```{r}
# Recoding depressive symptoms at age 16 
# ccs4500 - ccs4515 = depression data

data2_new <- data2 %>%
  mutate(across(ccs4500:ccs4515, ~ as.numeric(.))) %>% # recode as numerical
  mutate(across(ccs4500:ccs4515, ~ 3 - .)) %>% # reverse coding
  mutate(TotalDep = rowSums(select(., ccs4500, ccs4502, ccs4503, ccs4504, ccs4505, ccs4506, ccs4508, ccs4509, ccs4511, ccs4512, ccs4513, ccs4514, ccs4515), na.rm = FALSE)) %>%
  mutate(MaternalHighEd = ifelse(c645a == "A level" | c645a == "Degree", 1, 0))


data2_new
describe(data2_new)
summary(data2_new)


```

# DEB 16 presence during past 12 months
```{r}
# Coding DEB age 16 present during the past 12 months
data3 <- data2_new %>%
  mutate(Fast16 = 
           ifelse(ccs5520 == "Never",0,1)) %>% 
  mutate(Vomit = 
           ifelse(ccs5530 == "Never",0,1)) %>% 
  mutate(Laxatives = 
           ifelse(ccs5540 == "Never", 0,1)) %>% 
  mutate(Purge16 = 
           ifelse(Vomit == 1|Laxatives == 1, 1,0)) %>%
  mutate(Exercise16 = 
           ifelse((ccs5510 != "Never" & ccs5512 == "Yes, frequently" ) & ((ccs5513 =="Yes, frequently" | ccs5513 == "Do not miss any   exercise sessions") | ccs5511 == "Yes, frequently"), 1, 0)) %>%
  mutate(Binge16 = 
           ifelse(ccs5550 != "Never" & ccs5560 == "Yes, usually", 1, 0)) %>%
  mutate(AnyDEB16 = 
           ifelse(Fast16 == 1|Purge16 == 1|Exercise16 == 1|Binge16 == 1, 1,0)) %>%
  select(ID,Age,Sex,Ethnicity,MaternalHighEd,TotalDep,AMStotal,Fast16,Purge16,Exercise16,Binge16,AnyDEB16,PosAMS,NegAMS)

data3

data3_prep <- data3 %>% 
  select(-c(ID,Age)) %>%
  mutate_at(
    c(
      "Sex",
      "Ethnicity",
      "MaternalHighEd",
      "Fast16",
      "Purge16",
      "Exercise16",
      "Binge16",
      "AnyDEB16"
    ),
    as.factor
  )

summary(data3_prep)
```


# DEB 16 more than once a month
```{r}
# Coding DEB age 16 more than once a month
data3_c <- data2_new %>%
  mutate(Fast16 = 
           ifelse((ccs5520 == "1-3 times a month" | ccs5520 == "Once a week" | ccs5520 == "2 or more a week" ),1,0)) %>% 
  mutate(Vomit = 
           ifelse((ccs5530 == "1-3 times a month" | ccs5530 == "Once a week" | ccs5530 == "2-6 times a week" | ccs5530 == "Every day"),1,0)) %>% 
  mutate(YesLaxatives = 
           ifelse((ccs5540 == "Yes, laxative" | ccs5540 == "Yes, other"), 1,0)) %>%
  mutate(FreqLaxatives = 
           ifelse (YesLaxatives == 1 & (ccs5541 == "1-3 times a month" | ccs5541 == "Once a week"| ccs5541 == "2-6 times a week"|ccs5541 == "Every day"), 1,0)) %>% 
  mutate(Purge16 = 
           ifelse(Vomit == 1|FreqLaxatives == 1, 1,0)) %>%
  mutate(Exercise16 = 
           ifelse(((ccs5510 == "1-3 times a month" | 
                      ccs5510 == "1-4 times a week" | 
                      ccs5510 == "5 or more times a week") & 
                     ccs5512 == "Yes, frequently" ) & 
                    ((ccs5513 =="Yes, frequently" | ccs5513 == "Do not miss any exercise sessions") | 
                       ccs5511 == "Yes, frequently"), 1, 0)) %>%
  mutate(Binge16 = 
           ifelse(((ccs5550 != "Never") & (ccs5550 != "Less than once a month")) & ccs5560 == "Yes, usually", 1, 0)) %>%
  mutate(AnyDEB16 = 
           ifelse(Fast16 == 1|Purge16 == 1|Exercise16 == 1|Binge16 == 1, 1,0)) %>%
  select(ID,Age,Sex,Ethnicity,MaternalHighEd,TotalDep,AMStotal,Fast16,Purge16,Exercise16,Binge16,AnyDEB16)
data3_c

describe(data3_c)

data3c_prep <- data3_c %>% 
  select(-c(ID,Age)) %>%
  mutate_at(
    c(
      "Sex",
      "Ethnicity",
      "MaternalHighEd",
      "Fast16",
      "Purge16",
      "Exercise16",
      "Binge16",
      "AnyDEB16"
    ),
    as.factor
  )

summary(data3c_prep)

```

# DEB age 16 more than once a week
```{r}
# Coding DEB age 16 more than once a week
data3_w <- data2_new %>%
  mutate(Fast16 = 
           ifelse((ccs5520 == "Once a week" | ccs5520 == "2 or more a week" ),1,0)) %>% 
  mutate(Vomit = 
           ifelse((ccs5530 == "Once a week"|ccs5530 == "2-6 times a week"|ccs5530 == "Every day"),1,0)) %>% 
  mutate(YesLaxatives = 
           ifelse((ccs5540 == "Yes, laxative" | ccs5540 == "Yes, other"), 1,0)) %>%
  mutate(FreqLaxatives = 
           ifelse (YesLaxatives == 1 & (ccs5541 == "Once a week"| ccs5541 == "2-6 times a week"|ccs5541 == "Every day"), 1,0)) %>% 
  mutate(Purge16 = 
           ifelse(Vomit == 1|FreqLaxatives == 1, 1,0)) %>%
   mutate(Exercise16 = 
           ifelse(((ccs5510 == "1-4 times a week" | ccs5510 == "5 or more times a week") & ccs5512 == "Yes, frequently" ) & ((ccs5513 =="Yes, frequently" | ccs5513 == "Do not miss any exercise sessions") | ccs5511 == "Yes, frequently"), 1, 0)) %>%
  mutate(Binge16 = 
           ifelse((ccs5550 == "More than once a week" | ccs5550 == "Once a week") & ccs5560 == "Yes, usually", 1, 0)) %>%
  mutate(AnyDEB16 = 
           ifelse(Fast16 == 1|Purge16 == 1|Exercise16 == 1|Binge16 == 1, 1,0)) %>%
  select(ID,Age,Sex,Ethnicity,MaternalHighEd,TotalDep,AMStotal,Fast16,Purge16,Exercise16,Binge16,AnyDEB16) 
data3_w

describe(data3_w)

data3w_prep <- data3_w %>% 
  select(-c(ID,Age)) %>%
  mutate_at(
    c(
      "Sex",
      "Ethnicity",
      "MaternalHighEd",
      "Fast16",
      "Purge16",
      "Exercise16",
      "Binge16",
      "AnyDEB16"
    ),
    as.factor
  )

summary(data3w_prep)

```

# Check whether data is MCAR/MNAR
```{r}

# data3_prep: presence of DEB
aggr_plot <-
  aggr(
    data3_prep,
    col = c('skyblue', 'lightpink'),
    numbers = TRUE,
    sortVars = TRUE,
    labels = names(data3_prep),
    cex.axis = .7,
    gap = 3,
    ylab = c("Histogram of missing data", "Pattern")
  )

naniar::prop_miss(data3_prep) # 49.84% missing data in total
md.pattern(data3_prep) # N=3474 samples complete

# MAR?
explanatory = c("Sex", "Ethnicity", "MaternalHighEd", "AMStotal", "TotalDep")
dependent = "AnyDEB16"
data3_prep %>% 
  missing_pairs(dependent, explanatory)

# Recode variables 
data_MAR <- data3_prep %>% 
  mutate(naDEB = if_else(is.na(AnyDEB16), 0, 1))
data_MAR

amsMAR <- summary(glm(naDEB ~ AMStotal, data = data_MAR, family = binomial))
amsMAR_pvals <- amsMAR$coefficients[2, 4]
amsMAR_pvals
# AMS total predicts DEB NA values (specifically lower AMS predictive of DEB NA)

depMAR <- summary(glm(naDEB ~ TotalDep, data = data_MAR, family = binomial))
depMAR_pvals <- depMAR$coefficients[2, 4]
depMAR_pvals
# Depression does not predict DEB NA 


```

```{r}

# data3c_prep: presence of monthly DEB
aggr_plot <-
  aggr(
    data3c_prep,
    col = c('skyblue', 'lightpink'),
    numbers = TRUE,
    sortVars = TRUE,
    labels = names(data3c_prep),
    cex.axis = .7,
    gap = 3,
    ylab = c("Histogram of missing data", "Pattern")
  )

naniar::prop_miss(data3c_prep) # 51.73% missing data in total
md.pattern(data3c_prep) # N=3478 samples complete

# MAR?
explanatory = c("Sex", "Ethnicity", "MaternalHighEd", "AMStotal", "TotalDep")
dependent = "AnyDEB16"
data3c_prep %>% 
  missing_pairs(dependent, explanatory)

# Recode variables 
data_MARc <- data3c_prep %>% 
  mutate(naDEB = if_else(is.na(AnyDEB16), 0, 1))
data_MARc

amsMARc <- summary(glm(naDEB ~ AMStotal, data = data_MARc, family = binomial))
amsMARc_pvals <- amsMARc$coefficients[2, 4]
amsMARc_pvals
# AMS total predicts DEB NA values (specifically lower AMS predictive of DEB NA)

depMARc <- summary(glm(naDEB ~ TotalDep, data = data_MARc, family = binomial))
depMARc_pvals <- depMARc$coefficients[2, 4]
depMARc_pvals
# Depression does not predict DEB NA 


```

```{r}

# data3c_prep: presence of weekly DEB
aggr_plot <-
  aggr(
    data3w_prep,
    col = c('skyblue', 'lightpink'),
    numbers = TRUE,
    sortVars = TRUE,
    labels = names(data3w_prep),
    cex.axis = .7,
    gap = 3,
    ylab = c("Histogram of missing data", "Pattern")
  )

naniar::prop_miss(data3w_prep) # 51.73% missing data in total
md.pattern(data3w_prep) # N=3482 samples complete

# MAR?
explanatory = c("Sex", "Ethnicity", "MaternalHighEd", "AMStotal", "TotalDep")
dependent = "AnyDEB16"
data3w_prep %>% 
  missing_pairs(dependent, explanatory)

# Recode variables 
data_MARw <- data3w_prep %>% 
  mutate(naDEB = if_else(is.na(AnyDEB16), 0, 1))
data_MARw

amsMARw <- summary(glm(naDEB ~ AMStotal, data = data_MARw, family = binomial))
amsMARw_pvals <- amsMARw$coefficients[2, 4]
amsMARw_pvals
# AMS total predicts DEB NA values (specifically lower AMS predictive of DEB NA)

depMARw <- summary(glm(naDEB ~ TotalDep, data = data_MARw, family = binomial))
depMARw_pvals <- depMARw$coefficients[2, 4]
depMARw_pvals
# Depression does not predict DEB NA 


```

## MICE
```{r}
imp_method1 = c(
  "logreg", #Sex
  "polyreg", #Ethnicity
  "logreg", #MaternalHighEd
  "pmm", #TotalDep
  "pmm", #AMStotal
  "logreg", #Fast16
  "logreg", #Purge16
  "logreg", #Exercise16
  "logreg", #Binge16
  "logreg", #AnyDEB16
  "pmm", #PosAMS
  "pmm" #NegAMS
)

data3_imp <- mice(data3_prep,
              m = 20,
              method = imp_method,
              seed = 5000)
write.mice.imputation(data3_imp, name = "data3_imp_save", mids2spss = F)

```

```{r}
imp_method2 = c(
  "logreg", #Sex
  "polyreg", #Ethnicity
  "logreg", #MaternalHighEd
  "pmm", #TotalDep
  "pmm", #AMStotal
  "logreg", #Fast16
  "logreg", #Purge16
  "logreg", #Exercise16
  "logreg", #Binge16
  "logreg" #AnyDEB16
)

data3c_imp <- mice(data3c_prep,
              m = 20,
              method = imp_method2,
              seed = 5000)
write.mice.imputation(data3c_imp, name = "data3c_imp_save", mids2spss = F)

data3w_imp <- mice(data3w_prep,
              m = 20,
              method = imp_method2,
              seed = 5000)
write.mice.imputation(data3w_imp, name = "data3w_imp_save", mids2spss = F)

```

```{r}
load("data3_imp_save/data3_imp_save.Rdata")
data3_imp = mi.res
 
load("data3c_imp_save/data3c_imp_save.Rdata")
data3c_imp = mi.res
 
load("data3w_imp_save/data3w_imp_save.Rdata")
data3w_imp = mi.res
```

```{r}
#checking imp datasets

# data3
bwplot(data3_imp)
densityplot(data3_imp)
xyplot(data3_imp, AnyDEB16 ~ AMStotal | as.factor(.imp))

# data3c
bwplot(data3c_imp)
densityplot(data3c_imp)
xyplot(data3c_imp, AnyDEB16 ~ AMStotal | as.factor(.imp))

# data3w
bwplot(data3w_imp)
densityplot(data3w_imp)
xyplot(data3w_imp, AnyDEB16 ~ AMStotal | as.factor(.imp))

```


# Assumption Check with complete cases
```{r}
# Create model
model1 <- glm(AnyDEB16 ~ AMStotal + TotalDep + MaternalHighEd + Sex, data = data3_prep, family = binomial)

# No high multicolinearity
vif(model1) #variables are not really correlated

# influential values
plot(model1, which = 4, id.n = 3)

model1.data <- augment(model1) %>% 
  mutate(index = 1:n()) 

model1.data %>% top_n(3, .cooksd)

ggplot(model1.data, aes(index, .std.resid)) + 
  geom_point(aes(), alpha = .5) +
  theme_bw()
model1.data %>% 
  filter(abs(.std.resid) > 3) # No influential outliers

# Absence of outliers
outlierTest(model1)

# Power

```

# Logistic Regression DEB16 - complete cases
```{r}
# Analysis age 16 #presence of any DEB
model1 <- glm(AnyDEB16 ~ AMStotal + TotalDep + MaternalHighEd + Sex, data = data3_prep, family = binomial)
summary(model1) 

logistic_coefficients_model1 <- 
  model1$coefficients %>%
  unclass() %>% 
  as.data.frame() %>% 
  rename('B' = '.') %>%
  mutate(expB = exp(B)) 

logistic_coefficients_model1 %>% 
  kable(digits = 3)

exp(coef(model1))
exp(cbind(Odds_Ratio = coef(model1), confint(model1)))
```

# Logistic Regression DEB16 - MI
```{r}
# Analysis age 16 #presence of any DEB
modelMI1 <- with(data3_imp, glm(AnyDEB16 ~ AMStotal + TotalDep + MaternalHighEd + Sex, family = binomial))
summary(pool(modelMI1)) 


```


# Logistic regression - presence of any DEB > once a month
```{r}
# Complete case analysis age 16 #presence of any DEB > once a month
model1_c <- glm(AnyDEB16 ~ AMStotal + TotalDep + MaternalHighEd + Sex, data = data3c_prep, family = binomial)
summary(model1_c) 

logistic_coefficients_model1_c <- 
  model1_c$coefficients %>%
  unclass() %>% 
  as.data.frame() %>% 
  rename('B' = '.') %>%
  mutate(expB = exp(B))         

logistic_coefficients_model1_c %>% 
  kable(digits = 3)

exp(coef(model1_c))
exp(cbind(Odds_Ratio = coef(model1_c), confint(model1_c)))

```

# Logistic Regression DEB16 - presence of any DEB > once a month - MI 
```{r}
# Analysis age 16 #presence of any DEB
modelMI1_c <- with(data3c_imp, glm(AnyDEB16 ~ AMStotal + TotalDep + MaternalHighEd + Sex, family = binomial))
summary(pool(modelMI1_c)) 


```


# AMS & Separate DEB 16
```{r}
# Fasting
model1_Fast <- glm(Fast16 ~ AMStotal + TotalDep + MaternalHighEd + Sex, data = data3_prep, family = binomial)
summary(model1_Fast)
exp(coef(model1_Fast))
exp(cbind(Odds_Ratio = coef(model1_Fast), confint(model1_Fast)))

# Binge eating
model1_Binge <- glm(Binge16 ~ AMStotal+ TotalDep + MaternalHighEd + Sex, data = data3_prep, family = binomial)
summary(model1_Binge)
exp(coef(model1_Binge))
exp(cbind(Odds_Ratio = coef(model1_Binge), confint(model1_Binge)))

# Purging
model1_Purge <- glm(Purge16 ~ AMStotal+ TotalDep + MaternalHighEd + Sex, data = data3_prep, family = binomial)
summary(model1_Purge)
exp(coef(model1_Purge))
exp(cbind(Odds_Ratio = coef(model1_Purge), confint(model1_Purge)))

# Excessive exercise
model1_Exercise <- glm(Exercise16 ~ AMStotal+ TotalDep + MaternalHighEd + Sex, data = data3_prep, family = binomial)
summary(model1_Exercise)
exp(coef(model1_Exercise))
exp(cbind(Odds_Ratio = coef(model1_Exercise), confint(model1_Exercise)))

```


# AMS & Separate DEB 16 - MI
```{r}
# Fasting
modelMI1_Fast <- with(data3_imp, glm(Fast16 ~ AMStotal + TotalDep + MaternalHighEd + Sex, family = binomial))
summary(pool(modelMI1_Fast))

# Binge eating
modelMI1_Binge <- with(data3_imp, glm(Binge16 ~ AMStotal+ TotalDep + MaternalHighEd + Sex, family = binomial))
summary(pool(modelMI1_Binge))

# Purging
modelMI1_Purge <- with(data3_imp, glm(Purge16 ~ AMStotal+ TotalDep + MaternalHighEd + Sex, family = binomial))
summary(pool(modelMI1_Purge))

# Excessive exercise
modelMI1_Exercise <- with(data3_imp, glm(Exercise16 ~ AMStotal+ TotalDep + MaternalHighEd + Sex, family = binomial))
summary(pool(modelMI1_Exercise))

```


# Exploratory Analysis - DEB16 by memory valence
```{r}
# Positive AMS
model1Pos <- glm(AnyDEB16 ~ PosAMS + TotalDep + MaternalHighEd + Sex, data = data3_prep, family = binomial)
summary(model1Pos) 

logistic_coefficients_model1Pos <- 
  model1Pos$coefficients %>%
  unclass() %>% 
  as.data.frame() %>% 
  rename('B' = '.') %>%
  mutate(expB = exp(B))         

exp(coef(model1Pos))
exp(cbind(Odds_Ratio = coef(model1Pos),
          confint(model1Pos)))

# Negative AMS
model1Neg <- glm(AnyDEB16 ~ NegAMS + TotalDep + MaternalHighEd + Sex, data = data3_prep, family = binomial)
summary(model1Neg) 

logistic_coefficients_model1Neg <- 
  model1Neg$coefficients %>%
  unclass() %>% 
  as.data.frame() %>% 
  rename('B' = '.') %>%
  mutate(expB = exp(B))         

exp(coef(model1Neg))
exp(cbind(Odds_Ratio = coef(model1Neg),
          confint(model1Neg)))
```

# Exploratory Analysis - DEB16 by memory valence - MI
```{r}
# Positive AMS
modelMI1Pos <- with(data3_imp, glm(AnyDEB16 ~ PosAMS + TotalDep + MaternalHighEd + Sex, family = binomial))
summary(pool(modelMI1Pos)) 

# Negative AMS
modelMI1Neg <- with(data3_imp, glm(AnyDEB16 ~ NegAMS + TotalDep + MaternalHighEd + Sex, family = binomial))
summary(pool(modelMI1Neg)) 

```

#DEB at age 18 (presence of DEB during past 12 months)
```{r}
# Coding DEB for age 18 presence during past 12 months
data4 <- data2_new %>%
  rename(ID = cidB3980, 
         Age = ccm991a, 
         Sex = kz021,
         Ethnicity = c804) %>%
  mutate(Fast18 = 
           ifelse(cct4110 == "Never",0,1)) %>% 
  mutate(Vomit18 = 
           ifelse(cct4112 == "Never",0,1)) %>% 
  mutate(Laxatives18 = 
           ifelse(cct4115 == "Never", 0,1)) %>% 
  mutate(Purge18 = 
           ifelse(Vomit18 == 1|Laxatives18 == 1, 1,0)) %>%
  mutate(Exercise18 = 
           ifelse((cct4105 != "Never" & 
                    cct4107 == "Yes frequently") & ((cct4108 == "Yes frequently" |
                                                       cct4108 == "Do not miss any exercise sessions")|
                                                       cct4106 == "Yes frequently"), 1, 0)) %>%
  mutate(Binge18 = ifelse(cct4120 != "Never" & cct4125 == "Yes, usually",1,0)) %>%
  mutate(AnyDEB18 = ifelse(Fast18 == 1|Purge18 == 1|Exercise18 == 1|Binge18 == 1, 1,0)) %>%
  select(ID,Age,Sex,MaternalHighEd,AMStotal,Fast18,Purge18,Exercise18,Binge18,AnyDEB18,Total_LoC,TotalDep,Ethnicity,NegAMS) %>%
  filter(complete.cases(Total_LoC,AnyDEB18,TotalDep,MaternalHighEd,AMStotal)) 
data4
#Total_LoC,AnyDEB18,TotalDep,MaternalHighEd,AMStotal
```

```{r}
describe(data4)
summary(data4)
sum(data4$MaternalHighEd == TRUE)
sum(data4$MaternalHighEd == FALSE)
sum(data4$Fast18 == TRUE, na.rm = TRUE)
sum(data4$Purge18 == TRUE, na.rm = TRUE)
sum(data4$Binge18 == TRUE, na.rm = TRUE)
sum(data4$Exercise18 == TRUE, na.rm = TRUE)
sum(data4$AnyDEB18 == TRUE, na.rm = TRUE)

descriptives18 <- data4 %>%
  group_by(Sex) %>%
  summarise(n_AnyDEB16 = sum(AnyDEB18, na.rm = TRUE),
            n_Fast16 = sum(Fast18, na.rm = TRUE),
            n_Purge16 = sum(Purge18, na.rm = TRUE),
            n_Binge16 = sum(Binge18, na.rm = TRUE),
            n_Exercise16 = sum(Exercise18, na.rm = TRUE))
descriptives18
```

#DEB at age 18 (presence of DEB > once a month)
```{r}
# Coding DEB for age 18 > once a month during past 12 months
data4_c <- data2_new %>%
  rename(ID = cidB3980, 
         Age = ccm991a, 
         Sex = kz021,
         Ethnicity = c804) %>%
  mutate(Fast18 = 
           ifelse(cct4110 == "Once a week"|
                    cct4110 == "2 or more times a week" | 
                    cct4110 ==  "1-3 times a month",1,0)) %>% 
  mutate(Vomit18 = 
           ifelse(cct4112 == "Once a week"|
                  cct4112 == "2-6 times a week"|
                  cct4112 == "1-3 times a month"|
                  cct4112 == "Every day",1,0)) %>% 
  mutate(YesLaxatives = 
           ifelse(cct4115 == "Yes, laxative"|
                    cct4115 == "Yes, other", 1,0)) %>%
  mutate(LaxativesFreq = 
           ifelse(cct4116 == "1-3 times a month"|
                  cct4116 == "Once a week"|
                  cct4116 == "Every day"|
                  cct4116 == "2-6 times a week",
                  1,0)) %>%
  mutate(Laxatives18 = 
           ifelse(YesLaxatives == 1 & 
                    LaxativesFreq == 1, 1,0)) %>%
  mutate(Purge18 = 
           ifelse(Vomit18 == 1|Laxatives18 == 1, 1,0)) %>%
  mutate(Exercise18 = 
           ifelse(((cct4105 == "5 or more times a week"|
                    cct4105 == "1-4 times a week"|
                    cct4105 == "1-3 times a month") & 
                    cct4107 == "Yes frequently") & ((cct4108 == "Yes frequently" |
                                                       cct4108 == "Do not miss any exercise sessions")|
                                                       cct4106 == "Yes frequently"), 1, 0)) %>%
  mutate(Binge18 = ifelse((cct4120 == "1-3 times a month"|
                            cct4120 == "More than once a week"|
                            cct4120 == "Once a week") & 
                            cct4125 == "Yes, usually",1,0)) %>%
  mutate(AnyDEB18 = ifelse(Fast18 == 1|Purge18 == 1|Exercise18 == 1|Binge18 == 1, 1,0)) %>%
  select(ID,Age,Sex,MaternalHighEd,AMStotal,Fast18,Purge18,Exercise18,Binge18,AnyDEB18,Total_LoC,TotalDep) %>%
  filter(complete.cases(Total_LoC,AnyDEB18,TotalDep,MaternalHighEd,AMStotal)) 
data4_c
```

```{r}
describe(data4_c)
summary(data4_c)
sum(data4_c$Fast18 == TRUE, na.rm = TRUE)
sum(data4_c$Purge18 == TRUE, na.rm = TRUE)
sum(data4_c$Binge18 == TRUE, na.rm = TRUE)
sum(data4_c$Exercise18 == TRUE, na.rm = TRUE)
sum(data4_c$AnyDEB18 == TRUE, na.rm = TRUE)

descriptives18_monthly <- data4_c %>%
  group_by(Sex) %>%
  summarise(n_AnyDEB16 = sum(AnyDEB18, na.rm = TRUE),
            n = n(),
            n_Fast16 = sum(Fast18, na.rm = TRUE),
            n_Purge16 = sum(Purge18, na.rm = TRUE),
            n_Binge16 = sum(Binge18, na.rm = TRUE),
            n_Exercise16 = sum(Exercise18, na.rm = TRUE),
            meanAMS = mean(AMStotal,na.rm = TRUE),
            meanLOC = mean(Total_LoC,na.rm = TRUE),
            meanDepression = mean(TotalDep,na.rm = TRUE)
            )
descriptives18_monthly
```

#DEB at age 18 (presence of DEB > once a week)
```{r}
# Coding DEB for age 18 > once a week during past 12 months
data4_w <- data2_new %>%
  rename(ID = cidB3980, 
         Age = ccm991a, 
         Sex = kz021,
         Ethnicity = c804) %>%
  mutate(Fast18 = 
           ifelse(cct4110 == "Once a week"|
                    cct4110 == "2 or more times a week",1,0)) %>% 
  mutate(Vomit18 = 
           ifelse(cct4112 == "Once a week"|
                  cct4112 == "2-6 times a week"|
                  cct4112 == "Every day",1,0)) %>% 
  mutate(YesLaxatives = 
           ifelse(cct4115 == "Yes, laxative"|
                    cct4115 == "Yes, other", 1,0)) %>%
  mutate(LaxativesFreq = 
           ifelse(cct4116 == "Once a week"|
                  cct4116 == "Every day"|
                  cct4116 == "2-6 times a week",
                  1,0)) %>%
  mutate(Laxatives18 = 
           ifelse(YesLaxatives == 1 & 
                    LaxativesFreq == 1, 1,0)) %>%
  mutate(Purge18 = 
           ifelse(Vomit18 == 1|Laxatives18 == 1, 1,0)) %>%
  mutate(Exercise18 = 
           ifelse(((cct4105 == "5 or more times a week"|
                    cct4105 == "1-4 times a week") & 
                    cct4107 == "Yes frequently") & ((cct4108 == "Yes frequently" |
                                                       cct4108 == "Do not miss any exercise sessions")|
                                                       cct4106 == "Yes frequently"), 1, 0)) %>%
  mutate(Binge18 = ifelse((cct4120 == "More than once a week"|
                            cct4120 == "Once a week") & 
                            cct4125 == "Yes, usually",1,0)) %>%
  mutate(AnyDEB18 = ifelse(Fast18 == 1|Purge18 == 1|Exercise18 == 1|Binge18 == 1, 1,0)) %>%
  select(ID,Age,Sex,MaternalHighEd,AMStotal,Fast18,Purge18,Exercise18,Binge18,AnyDEB18,Total_LoC,TotalDep) %>%
  filter(complete.cases(Total_LoC,AnyDEB18,TotalDep,MaternalHighEd,AMStotal)) 
data4_w
```

```{r}
describe(data4_w)
summary(data4_w)
sum(data4_w$Fast18 == TRUE, na.rm = TRUE)
sum(data4_w$Purge18 == TRUE, na.rm = TRUE)
sum(data4_w$Binge18 == TRUE, na.rm = TRUE)
sum(data4_w$Exercise18 == TRUE, na.rm = TRUE)
sum(data4_w$AnyDEB18 == TRUE, na.rm = TRUE)
```

# Descriptives of participants at age 18
```{r}
data4 %>%
  select(Sex) %>%
  group_by(Sex) %>%
  summarise(n = n()) %>%
  ungroup()

data4 %>%
  select(Ethnicity) %>%
  group_by(Ethnicity) %>%
  summarise(n = n()) %>%
  ungroup()

data4 %>%
  select(MaternalHighEd) %>%
  group_by(MaternalHighEd) %>%
  summarise(n = n()) %>%
  ungroup()
```

# Association among AMS, LOC, and DEB at age 18
```{r}
model2_AMS_LOC <- glm(Total_LoC ~ AMStotal, data = data4)
summary(model2_AMS_LOC)
confint(model2_AMS_LOC)

modelLOC <- glm(AnyDEB18 ~ Total_LoC, data = data4, family = binomial)
summary(modelLOC)
exp(coef(modelLOC))
exp(cbind(Odds_Ratio = coef(modelLOC),
          confint(modelLOC)))

model2_AMS_DEB18 <- glm(AnyDEB18 ~ AMStotal, data = data4, family = binomial)
summary(model2_AMS_DEB18)
exp(coef(model2_AMS_DEB18))
exp(cbind(Odds_Ratio = coef(model2_AMS_DEB18),
          confint(model2_AMS_DEB18)))
```

# Assumption check for asssociation between AMS & LOC
```{r}
# linearity
crPlots(model2_AMS_LOC)

# independence of errors
plot(model2_AMS_LOC, which = 1)

# normality
qqnorm(resid(model2_AMS_LOC))
qqline

# no outliers
plot(model2_AMS_LOC, which = 5)

```


# Mediation (presence of DEB18) using PROCESS with covariates
```{r}
data4$SexN <- ifelse(data4$Sex == "Male", 0,1)
process(data = data4, y = "AnyDEB18", x = "AMStotal", m = "Total_LoC", cov = c("SexN","MaternalHighEd","TotalDep"), model = 4, boot = 10000, seed = 984037)
```

# Mediation (monthly DEB 18 using PROCESS)
```{r}
data4_c$SexN <- ifelse(data4_c$Sex == "Male", 1,0)
process(data = data4_c, y = "AnyDEB18", x = "AMStotal", m = "Total_LoC", cov = c("SexN","MaternalHighEd","TotalDep"), model = 4)
```

# Exploratory Mediation (NegAMS & AnyDEB 18 using PROCESS without covariates)
```{r}

process(data = data4, y = "AnyDEB18", x = "NegAMS", m = "Total_LoC", model = 4, boot = 10000)
```

# Exploratory Mediation (NegAMS & AnyDEB 18 using PROCESS with covariates)
```{r}
process(data = data4, y = "AnyDEB18", x = "NegAMS", m = "Total_LoC", cov = c("SexN","MaternalHighEd","TotalDep"), model = 4, boot = 10000)
```

# Mediation (weekly DEB 18 using PROCESS)
```{r}
data4_w$SexN <- ifelse(data4_w$Sex == "Male", 1,0)
process(data = data4_w, y = "AnyDEB18", x = "AMStotal", m = "Total_LoC", cov = c("SexN","MaternalHighEd","TotalDep"), model = 4)
```

# Mediation (presence of DEB18)
```{r}
# LoC mediation model
# Create the Model Syntax

modelDEB18 <- ' 

# Direct effects
AnyDEB18 ~ c*AMStotal + TotalDep + MaternalHighEd + Sex

# Mediator
Total_LoC ~ a*AMStotal + TotalDep + MaternalHighEd + Sex
AnyDEB18 ~ b*Total_LoC

# Indirect effect
ab := a*b

# Total effect
total := c + (a*b)
' 
fitDEB18<-sem(model = modelDEB18, data = data4, estimator = "MLR")
summary(fitDEB18)
parameterEstimates(fitDEB18, standardized = TRUE)
```

# Mediation (presence of monthly DEB18)
```{r}
# LoC mediation model
# Create the Model Syntax

modelDEB18 <- ' 

# Direct effects
AnyDEB18 ~ c*AMStotal + TotalDep + MaternalHighEd + Sex

# Mediator
Total_LoC ~ a*AMStotal + TotalDep + MaternalHighEd + Sex
AnyDEB18 ~ b*Total_LoC

# Indirect effect
ab := a*b

# Total effect
total := c + (a*b)
' 
fitDEB18<-sem(model = modelDEB18, data = data4_c, estimator = "MLR")
summary(fitDEB18)
parameterEstimates(fitDEB18, standardized = TRUE)
```